Comparing Genetic Architectures

### 2022-01-28 graphs_newt_snakes/Comparing_GA.Rmd
made a new graph to compare newt-snake pop size by plotting popsize with color and shape determined by the GAs in the simulation

  sumitup <- GA_file[ which(GA_file$gen>=1500 & GA_file$sim ==LETTERS[i]),]
  sumitup_20 <- GA_file_20[ which(GA_file_20$gen>=2500 & GA_file_20$sim ==LETTERS[i]),]
  params$Newt_mean_Pheno[i]<-mean(sumitup$Newt_mean_Pheno)
  params$Snake_mean_Pheno[i]<-mean(sumitup$Snake_mean_Pheno)
  params$Newt_pop_size[i]<-mean(sumitup$Newt_pop_size)
  params$Snake_pop_size[i]<-mean(sumitup$Snake_pop_size)
  params$dif[i]<-mean(sumitup$dif)
  params$Newt_mean_Pheno_20[i]<-mean(sumitup_20$Newt_mean_Pheno)
  params$Snake_mean_Pheno_20[i]<-mean(sumitup_20$Snake_mean_Pheno)
  params$Newt_pop_size_20[i]<-mean(sumitup_20$Newt_pop_size)
  params$Snake_pop_size_20[i]<-mean(sumitup_20$Snake_pop_size)
  params$dif_20[i]<-mean(sumitup_20$dif)

@@

>>>>

  sumitup <- GA_file[ which(GA_file$gen>=1500 & GA_file$sim ==LETTERS[i]),]
  sumitup_20 <- GA_file_20[ which(GA_file_20$gen>=3500 & GA_file_20$sim ==LETTERS[i]),]
  params$Newt_mean_Pheno[i]<-mean(sumitup$Newt_mean_Pheno)
  params$Snake_mean_Pheno[i]<-mean(sumitup$Snake_mean_Pheno)
  params$Newt_pop_size[i]<-mean(sumitup$Newt_pop_size)
  params$Snake_pop_size[i]<-mean(sumitup$Snake_pop_size)
  params$dif[i]<-mean(sumitup$dif)
  params$Newt_mean_Pheno_20[i]<-mean(sumitup_20$Newt_mean_Pheno)
  params$Snake_mean_Pheno_20[i]<-mean(sumitup_20$Snake_mean_Pheno)
  params$Newt_pop_size_20[i]<-mean(sumitup_20$Newt_pop_size)
  params$Snake_pop_size_20[i]<-mean(sumitup_20$Snake_pop_size)
  params$dif_20[i]<-mean(sumitup_20$dif)

@@

title="Space: Newt VS Snake Population Size"
subt="Gen 16sims"
y_label="Snake Popsize"
x_label="Newt Popsize"

params$newt_mu_effect_sd

params$snake <- paste0(params$snake_mu_rate, "_",params$snake_mu_effect_sd)
params$newt <- paste0(params$newt_mu_rate, "_",params$newt_mu_effect_sd)

t16 <- ggplot(params) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = subt) +
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = factor(snake), shape=factor(newt)),size=3)+
#  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  #facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
t16

t16g <- ggplot(params) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = "Gen 16sims 20000Gen") +
  xlab(x_label) + ylab(y_label)+
  #geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = factor(snake), shape=factor(newt)))+
  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)), size=3)+
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  #facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
t16g

t16d <- ggplot(params) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = subt) +
  xlab(x_label) + ylab("DIF: s-n")+
  #geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = factor(snake), shape=factor(newt)))+
  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(dif), color = factor(snake), shape=factor(newt)), size=3)+
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  #facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
t16d

t16d2 <- ggplot(params) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = subt) +
  xlab("Snake pop size") + ylab("DIF: s-n")+
  #geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = factor(snake), shape=factor(newt)))+
  geom_point(aes(x=as.numeric(Snake_pop_size), y=as.numeric(dif), color = factor(snake), shape=factor(newt)), size=3)+
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  #facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
t16d2
